### 2009-07-09 docs/architecture/architecture.tex
fixed type multifab_types --> multifab_module

\noindent Here, the {\tt bl\_types} and {\tt multifab\_types} modules
bring in the basic boxlib data types Specifically, here, {\tt
bl\_types} defines {\tt dp\_t} which is the {\tt kind} used for
declaring double precision data, and {\tt multifab\_module} defines
the \multifab\ data type.  The {\tt geometry} module is a MAESTRO
module that provides the dimensionality ({\tt dm}) and the number of 
levels ({\tt nlevs}).  The {\tt variables} module is a MAESTRO
module that provides integer keys for indexing the state arrays.  In
this case the integer {\tt rho\_comp} refers to the location in the
state array corresponding to density.

>>>>

\noindent Here, the {\tt bl\_types} and {\tt multifab\_module} modules
bring in the basic boxlib data types Specifically, here, {\tt
bl\_types} defines {\tt dp\_t} which is the {\tt kind} used for
declaring double precision data, and {\tt multifab\_module} defines
the \multifab\ data type.  The {\tt geometry} module is a MAESTRO
module that provides the dimensionality ({\tt dm}) and the number of 
levels ({\tt nlevs}).  The {\tt variables} module is a MAESTRO
module that provides integer keys for indexing the state arrays.  In
this case the integer {\tt rho\_comp} refers to the location in the
state array corresponding to density.
